DRAFT: Extracting Comments From MS Word DOCX Files

### 2019-05-17 docxcommentextraction.Rmd
update

---
title: "DRAFT: DOCX Comment Extraction"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The testing dataset used in this project was created using BaSH scripting and one-off text processing. This page documents progress on building a workflow to replicate that process using R tools.

@@

#General Approach
*  Create a list of files to cycle through OR put all files to process in ONE folder. 
*  For each file, use 'read_docx', then 'docx_extract_all_cmnts'. 
*  Use 'do.call("rbind", list(dataframes to merge))' to cycle through and append the extracted comments to ONE dataframe

#Code Sources, Examples

https://stackoverflow.com/questions/50439684/how-to-extract-plain-text-from-docx-file-using-r

https://stackoverflow.com/questions/5965698/merge-unequal-dataframes-and-replace-missing-rows-with-0

https://stat.ethz.ch/R-manual/R-devel/library/base/html/merge.html

https://www.dummies.com/programming/r/how-to-use-the-merge-function-with-data-sets-in-r/

https://datascienceplus.com/combining-data-in-r-the-skill-of-merging-joining-and-stacking/

https://www.rdocumentation.org/packages/analogue/versions/0.17-1/topics/join
Load required Libraries

#Sample Working Code
```{}
library(docxtractr)
```

Call in Word files using ```read_docx```. Use ```docx_extract_all_cmts``` to pull out comments and ```rbind``` to combine them.

To merge more than two dataframes within R, combine an ```rbind``` call with ```do.call```. The 'do.call' function uses any existing R functions, such as 'rbind', but instead of passing just two dataframes, it passes multiple data frames. Then use ```write.csv2``` to write the data to a CSV format.

```{}
Commentframe1<-read_docx("/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/DOCX_comment_extraction/TestingReport.docx", track_changes = NULL)
comments1<-docx_extract_all_cmnts(Commentframe1, include_text = FALSE)

Commentframe2<-read_docx("/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/DOCX_comment_extraction/TestingCommentExtraction.docx", track_changes = NULL)
comments2<-docx_extract_all_cmnts(Commentframe2, include_text = FALSE)

# comments1And2 <- rbind(comments1,comments2)
# OR
# comments1And2 <- do.call("rbind", list(comments1,comments2))

#Check data have been successfully merged by checking the number of rows
NROW(comments1And2)
# [1] 32

#When all lines are appended, write the CSV file 
write.csv2(comments1And2, file = "TAcomments.csv")

>>>>

---
title: "DRAFT: Extracting Comments From MS Word DOCX Files"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The testing dataset used in to build this project was created using BaSH scripting and one-off text processing. This page documents progress on building an R-based repeatable workflow to simplify that process.

@@

#General Approach
*  Put all files to process in ONE folder. 
*  Extract a list of file names to cycle through.
*  For each file, use 'read_docx', then 'docx_extract_all_cmnts'. 
*  Cycle through and append the extracted comments to ONE dataframe

```{r Libraries}
library(plyr)
library(tidyverse)
library(reshape2)
library(tidyr)
library(readtext)
library(docxtractr)
```

```{r List_Files}
#Generates a list of all files in a particular folder
files_list <-list.files("~/Dropbox/Coding_Tools/R_Environment/R_Projects/DOCX_comment_extraction/Test_Set", full.names=TRUE)
```

```{r Pull the comments}
#### load data ####
# Define path of directory
# Get full path filename of every .docx-file in directory as 'filelist'
# Get filenames without paths for same sequence as 'filelist_short'
pathto <- "~/Dropbox/Coding_Tools/R_Environment/R_Projects/DOCX_comment_extraction/Test_Set/Hiding"
filelist <- list.files(path = pathto, pattern = "*.docx", full.names = TRUE)
filelist_short <- list.files(path = pathto, pattern = "*.docx", full.names = FALSE)

# Read every file with docxtractr::read_docx()
# Extract every comment from every file with docxtractr::docx_extract_all_cmnts()
document_contents_list <- lapply(filelist, read_docx)
comments_list <- lapply(document_contents_list, docx_extract_all_cmnts, include_text=TRUE)

The variable named 'comments_list' is a  list of length 6. Each item in the list is a tibble with variable number of rows, but all with the same 6 columns:

*  id
*  author
*  date
*  initials
*  comment_text
*  word_src

I need to append each tibble to the next one for all items in the list.

```{r Bind together the individual items in the comments_list List}

# identify the filename of the docx file that was used to create the list of comments
document_contents_list[[3]]$path

# join the individual lists of comments into a larger list
comments_list_joined <- bind_rows(comments_list, id=NULL)

# problem is that I lose the filenames.

***
Problem to solve now is the joined comments list contains no record of the source file's name. Need some way to attach the remaining report metadata.
***

```{r Write CSV}
#Creates the output CSV file if needed for analysis outside R.
write.csv(comments_list_joined, file = "~/Dropbox/Coding_Tools/R_Environment/R_Projects/DOCX_comment_extraction/Test_Set/Extracted_comments.csv")
```

```{}

#Rename the columns in a data.frame. In this example, "name" has 2 columns. The command pipes new names to the 2 columns, using the vectorized text names.
names(name_of_file_to_change) <- c("columns", "values")
